### 2022-03-08 README.Rmd
switch to using targets

-   Open the project in RStudio by double-clicking the `.Rproj` file.
-   Install packages listed in `packages.R` (if this compendium uses `renv`, this may happen automatically or with `renv::restore()`).
-   Run scripts in /R/ in numerical order.
-   Knit /doc/paper.Rmd to produce output

<!-- Additional instructions if project uses `targets`: -->

<!-- -   Install the [`targets` package](https://docs.ropensci.org/targets/). -->

<!-- -   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs. -->

<!-- **NOTE**: the GitHub actions in .github/workflows/build-manuscript.yaml will not work with a `targets` project. -->

<!-- Consider `targets::tar_github_actions()` as an alternative -->

>>>>

-   Open the project in RStudio by double-clicking the `.Rproj` file.
-   Install packages listed in `packages.R` (if this compendium uses `renv`, this may happen automatically or with `renv::restore()`).
-   Install the [`targets` package](https://docs.ropensci.org/targets/).
-   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs.

<!-- Consider using `targets::tar_github_actions()` if targets aren't too big -->
